### 2019-08-06 1_introduction.tex
Add a takeaway to intro, and cuts elsewhere to make space.

Adding a new programming system to Task Bench involves  implementing a set of standard
services, such as executing a task or a data transfer.  This interface is simple enough to 
be implemented with reasonable effort to a level of quality sufficient for comparative
studies. Task Bench provides a core library that encapsulates the functionality
shared among systems, which not only reduces the implementation effort
required but also makes it much easier to achieve truly apples-to-apples comparisons
between systems.

Using Task Bench we were able to quickly incorporate 15 very different parallel and distributed
runtime systems.  By running all systems on common benchmarks we were able to quantify phenomena
that have never before been measured.
Most strikingly, the performance of the systems we examine varies by more than five orders
of magnitude, with very popular, widely used systems at both ends of the spectrum!  Clearly
the slower systems have ``good enough'' performance for some class of applications, while presumably
providing advantages in programmer productivity.

This result points to a natural question:   How does one predict whether the performance of a runtime
system will in fact be good enough for a particular application?  In trying to answer this question,
we realized that \emph{weak} and \emph{strong} scaling, by far the most commonly
reported performance metrics, do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from costs
(such as increased communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

A lower METG does not necessarily mean that
performance for a particular workload is better. For example, two systems with METG(50\%) of 100~\textmu{}s and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both very likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) will performance
likely diverge. Thus METG helps to identify the regime in which a
given system can deliver good performance, and explains how
different systems coexist with runtime overheads that vary by orders of magnitude.

@@

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While in the most simplified scenarios, some systems can
achieve a METG(50\%) of 390~ns, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies.

>>>>

Adding a system to Task Bench involves  implementing a set of standard
services, such as executing a task or data transfer, simple enough to 
be implemented with reasonable effort to a level of quality sufficient for comparative
studies. Task Bench provides a core library that encapsulates functionality
shared among systems, which not only reduces implementation effort
but also makes it much easier to achieve truly apples-to-apples comparisons
between systems.

Using Task Bench we were able to quickly incorporate 15 very different parallel and distributed
programming systems.  By running all systems on common benchmarks we were able to quantify phenomena
that have never before been measured.
Most strikingly, the overheads of the systems we examine vary by more than five orders
of magnitude, with popular, widely used systems at both ends of the spectrum!  Clearly
the slower systems have ``good enough'' performance for some class of applications, while presumably
providing advantages in programmer productivity.

How does one predict whether the performance of a given
system will be good enough for a particular application?  In trying to answer this question,
we realized that \emph{weak} and \emph{strong} scaling, by far the most commonly
reported performance metrics, do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from costs
(such as increased communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

A lower METG does not necessarily mean that
performance for a particular workload is better. Two systems with METG(50\%) of 100~\textmu{}s and 1~ms,
respectively, running an application with 10~ms average task granularity, are both likely to perform well. Only when task
granularity approaches (or drops below) METG(50\%) will they
likely diverge. METG identifies the regime in which a
given system can deliver good performance, and explains how
different systems coexist with runtime overheads that vary by orders of magnitude.

@@

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While in the most simplified scenarios, some systems can
achieve a METG(50\%) of 390~ns, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. We find asynchronous systems provide benefits
(e.g., overlapping compute and communication), but only if system overheads do not exceed roughly
100~\textmu{}s.
